Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2024-04-13 LaTeX_paper/paper.tex
minor fixes

The most promising approach to improving the Comparator
involves utilizing machine learning, but this requires a substantial amount of data.
Conversely, creating a better Solver is a less straightforward task.
However, if successful, it could potentially serve as a labeling tool
to generate the dataset needed to train a superior Comparator.

@@

\subsection{Context}
This section will provide some basic knowledge
related to the jigsaw problem that will be useful
  for the next sections.
\subsubsection{Classification}
Puzzles are categorized in different types, for example 
\begin{itemize}
  \item Type 1 puzzles have the orientation of the pieces known, but the position unknown. 
  \item Type 2 puzzles have both the orientation and the position of the pieces unknown.
  \item Type 3 puzzles have the orientation of the pieces unknown, but the position known.
\end{itemize}
Between these categories type 2 are the hardest, and will be the focus of this paper.

@@

There is  another important distinction between different types of puzzles.
They can be divided into “digital”~\cref{fig:figure_digital_puzzle} and
“real world”~\cref{fig:figure_real_puzzle} jigsaw puzzles.
The difference between the two is quite self explanatory,
and can be observed in the respective pictures.
\label{document:DigitalVSReal}

@@

The reason this distinction is important is because,
despite the generic concept of the puzzle not changing,
obtaining accurate matches of a piece's characteristics
is far easier with a digital puzzle,
since there are far fewer things that can go wrong.
For example, a piece's shape may be distorted by
a low-quality cut, as seen in picture~\cref{fig:figure_measurement_error}

@@

    \subsubsection{The Solver:} This component utilizes the information provided by the
    Comparator~\cref{document:comparator}, and attempts to find a solution
    (i.e.\ a position and an orientation for each piece)
    that is the most likely to be correct.\label{document:solver}

@@

	To answer this question we will measure the accuracy of the comparator we developed
  and observe what would happen if that accuracy is
  applied to a digital puzzle solver. We will then propose a solution to improve
  the accuracy of real-world Comparators.

@@

This section will describe the implementation of the puzzle solver we developed.
This solver will then be put to the test in the next section.

@@

The next step following the general structure~\cref{document:splitter}
is to split a piece into
his 4 sides, this can be done with the following steps:

@@

\subsection{Our Solver}\label{document:my_solver}
The Solver that has been developed is not the primary focus of this
paper and cannot be considered state-of-the-art when compared
to the current best digital puzzle solvers. However, it may be
considered as such when compared to existing ``real-world'' puzzle solvers.

@@

\subsubsection{Basic Components}
To implement the algorithm two fundamental object are defined
\begin{itemize}
  \item \texttt{SinglePiece}: which contains information about a single puzzle piece.
  \item P\texttt{PieceGroup\(<\)T\(>\)} where \texttt{T} can be either a \texttt{PieceGroup} or a \texttt{SinglePiece}\newline
  This element encompasses four elements of type \texttt{T}, each with its own position (top right, top left, bottom left, bottom right).
\end{itemize}
Both \texttt{SinglePiece} and \texttt{PieceGroup} have an ``orientation'' attribute that goes from 0 to 3~\cref{fig:orientation}.
\begin{figure}[H]
  \caption{orientation attribute of an object}\label{fig:orientation}
  \centering
  \includegraphics[height=0.3\textwidth]{pictures/orientation.png}
\end{figure}

@@

The constants MIN\_SHORE\_SINGLE\_SIDE and MIN\_SHORE\_PIECE\_GROUP mentioned in
section~\cref{document:combining_four_objects} were set at different values
depending on the nature of the puzzle (real or digital).

@@

\subsubsection{Accuracy}
It is crucial to mention that the project currently lacks an automated
method for evaluating the accuracy of results. However, the accuracy
of two real-world puzzles (4x4 and 8x8) and one digital puzzle (16x16) has been manually confirmed,
with them achieving a 100\% correctness.

\begin{table}[H]
\centering
\begin{tabular}{
>{\columncolor[HTML]{FCE5CD}}c 
>{\columncolor[HTML]{FFF2CC}}c 
>{\columncolor[HTML]{EAD1DC}}c }
\multicolumn{3}{c}{\cellcolor[HTML]{EA9999}Manually evaluated accuracy of the solution}                       \\
\cellcolor[HTML]{F9CB9C}Puzzle size & \cellcolor[HTML]{FFE599}Puzzle kind & \cellcolor[HTML]{D5A6BD}Accuracy \\
4x4                                 & real world                          & 100\%                            \\
8x8                                 & real world                          & 100\%                            \\
16x16                               & digital                             & 100\%                           
\end{tabular}
\end{table}

@@

This paper has asserted from the beginning that real-world puzzles
pose greater challenges compared to their digital counterparts.
While some intuitive explanations were provided to support this assertion,
a proof hasn't been been presented until now. This test ultimately substantiates 
the claim, demonstrating that the performance of the same
algorithm can vary significantly depending on the accuracy of the input data.

@@

Unfortunately the conducted tests reveal that the Comparator developed
in this paper~\cref{document:my_comparator}
and the ``Graph Connection Laplacian'' solution~\cref{document:GCL}
are not compatible with each other.
A formal proof supporting this assertion is presented subsequently.

@@

The comparison algorithm deceived in section~\cref{document:my_comparator} outputs a compatibility
shore that goes from 0 to 1.\newline
But the algorithm~\cref{document:GCL} takes as input a binary value.
Which means that it is necessary to apply a threshold to the input
data to convert them from float to bool.

To find the optimal threshold a small 16 piece puzzle has been solved.
And the following 4 values have been measured, in function of the threshold:

@@

  \item \textbf{correct combination match\% (or c.c match\%):}\newline
  The probability that 2 randomly selected sides matches given that in the correct puzzle
  solution they are actually close to each other. Ideally this should be 1.

  \item \textbf{limit match\%:}\newline
  Given that this measures has been taken on a 16 piece puzzle,
  the match\% is highly influenced by the correct piece matching together.
  With a bigger puzzle the match\% would be lower (Given that the amount
  of correct couple of sides scales with N, while the amount of
  possible couple of sides scales with \(N^2\). Where N is the number of pieces).\newline
  Limit match\% is an approximation of what the match\%
  would be in the limit for \(N \rightarrow + \infty\).
  This value is obtained by subtracting to match\%
  the probability of choosing randomly the correct side,
  multiplied by the probability that the comparison returns true
  (which is c.c match\%). \newline
  Ideally limit match\% should be almost zero.
  \[limit \: math\% = math\% - \frac{c.c. \: mathc\%}{16 \times 4}\]

@@

Now, let's consider Algorithm \cref{document:GCL} tasked with solving a 500-piece puzzle
using our Comparator \cref{document:my_comparator}.
A threshold of 0.425 is chosen;
This implies a limit match\% of 0.04 and a corruption rate of 0.057.
What would this mean in terms of accuracy of the results?

@@

\subsubsection{Corruption Rate Analysis}
\begin{figure}[h]
  \caption{Neighbors comparison vs Corruption rate of algorithm \cref{document:GCL}. Image taken from pater \cite{GCL} page 34.}\label{fig:GCL_Corruption_Rate}
  \centering
  \includegraphics[height=0.35\textwidth]{pictures/corruption_rate.png}
\end{figure}

@@

Some minor improvements to the comparator can be made by spending some time
tweaking the current algorithm.
However, it is evident that for a task of this nature,
the most viable solution would likely involve
leveraging machine-learning techniques.

@@

\paragraph {Basic notions}

One piece is uniquely identified by his id piece\_id.
The id is an integer that goes from 0 to \mbox{Number of pieces - 1}.
Each piece has 4 sides that can be identified by the side side\_id,
an integer that goes from 0 to 3.

\paragraph {Image of each piece}

Inside the folder results/pieces the program will generate one image
for each one of the pieces of the puzzle. The file will be named \{piece\_id\}.jpeg.
An example can be seen in \cref{fig:result_pieces}

@@

\paragraph {Image of each side}

Inside the folder results/sides the program will generate one image 
for each side of each piece. The images will be named \{piece\_id\}\_\{side\_id\}.jpeg.
An example can be seen in \cref{fig:result_sides}

@@

\paragraph{Corners of each piece}
The file corners.json will be generated inside the folder results.
This file will contain a list of pieces.
Each piece has 4 sides, and each side has the coordinates of the two points
that delimit itself.\newline
An example of the generated json can be seen below.

@@

\paragraph{Match for each side}
The file connections\_result.json will be generated
inside the folder results. This file will contain a list of pieces,
each piece has 4 sides, and each side has a link to the side of the piece
that matches it. The link can be null if the side is along the border.\newline
An example of the generated json can be seen below.

@@

>>>>

The most promising approach to improve the Comparator
involves utilizing machine learning, but this requires a substantial amount of data.
Conversely, creating a better Solver is a less straightforward task.
However, if successful, it could potentially serve as a labeling tool
to generate the dataset needed to train a superior Comparator.

@@

\subsection{Context}
This section will provide some basic knowledge
related to the jigsaw problem that will be useful
  for the next sections.
\subsubsection{Classification}
Puzzles are categorized in different types, for example:
\begin{itemize}
  \item Type 1 puzzles have the orientation of the pieces known, but the position unknown. 
  \item Type 2 puzzles have both the orientation and the position of the pieces unknown.
  \item Type 3 puzzles have the orientation of the pieces unknown, but the position known.
\end{itemize}
Between these categories type 2 are the hardest, and will be the focus of this paper.

@@

There is  another important distinction between different types of puzzles.
They can be divided into “digital” e.g.~\cref{fig:figure_digital_puzzle} and
“real world” e.g.~\cref{fig:figure_real_puzzle} jigsaw puzzles.
The difference between the two is quite self explanatory,
and can be observed in the respective pictures.
\label{document:DigitalVSReal}

@@

The reason this distinction is important is because,
despite the generic concept of the puzzle not changing,
obtaining accurate measures of a piece's characteristics
is far easier with a digital puzzle,
since there are far fewer things that can go wrong.
For example, a piece's shape may be distorted by
a low-quality cut, as seen in~\cref{fig:figure_measurement_error}

@@

    \subsubsection{The Solver:} This component utilizes the information provided by the
    Comparator, and attempts to find a solution
    (i.e.\ a position and an orientation for each piece)
    that is the most likely to be correct.\label{document:solver}

@@

	To answer this question we will measure the accuracy of the comparator we developed
  and observe what would happen if that accuracy is
  applied to a digital puzzle Solver. We will then propose a solution to improve
  the accuracy of real-world Comparators.

@@

This section will describe the implementation of the puzzle solver we developed.
This solver will then be put to the test in the next sections.

@@

The next step following the general structure described in~\cref{document:splitter}
is to split a piece into
his 4 sides, this can be done with the following steps:

@@

\subsection{Our Solver}\label{document:my_solver}
The Solver we developed cannot be considered state-of-the-art when compared
to the current best digital puzzle solvers. However, it may be
considered as such when compared to existing ``real-world'' puzzle solvers.

Regardless, the achieved performances are still good enough to test and understand
the differences between digital and real-world puzzles,
which is the main objective of this paper.

@@

\subsubsection{Basic Components}
To implement the algorithm two fundamental object are defined
\begin{itemize}
  \item \texttt{SinglePiece}: which contains information about a single puzzle piece.
  \item P\texttt{PieceGroup\(<\)T\(>\)} where \texttt{T} can be either a \texttt{PieceGroup} or a \texttt{SinglePiece}\newline
  This element encompasses four elements of type \texttt{T}, each with its own position (top right, top left, bottom left, bottom right).
\end{itemize}
Both \texttt{SinglePiece} and \texttt{PieceGroup} have an ``orientation'' attribute that goes from 0 to 3, this attribute
represent the orientation of the piece, as shown in~\cref{fig:orientation}.
\begin{figure}[H]
  \caption{orientation attribute of an object}\label{fig:orientation}
  \centering
  \includegraphics[height=0.3\textwidth]{pictures/orientation.png}
\end{figure}

@@

The constants \texttt{MIN\_SHORE\_SINGLE\_SIDE} and \texttt{MIN\_SHORE\_PIECE\_GROUP} mentioned in
section~\cref{document:combining_four_objects} were set at different values
depending on the nature of the puzzle (real or digital).

@@

\subsubsection{Accuracy}
It is crucial to mention that the project currently lacks an automated
method for evaluating the accuracy of the results. However, the accuracy
of two real-world puzzles (4x4 and 8x8) and one digital puzzle (16x16) has been manually confirmed,
with them achieving a 100\% correctness.

\begin{table}[H]
\centering
\begin{tabular}{
>{\columncolor[HTML]{FCE5CD}}c 
>{\columncolor[HTML]{FFF2CC}}c 
>{\columncolor[HTML]{EAD1DC}}c }
\multicolumn{3}{c}{\cellcolor[HTML]{EA9999}Manually evaluated accuracy of the solutions}                       \\
\cellcolor[HTML]{F9CB9C}Puzzle size & \cellcolor[HTML]{FFE599}Puzzle kind & \cellcolor[HTML]{D5A6BD}Accuracy \\
4x4                                 & real world                          & 100\%                            \\
8x8                                 & real world                          & 100\%                            \\
16x16                               & digital                             & 100\%                           
\end{tabular}
\end{table}

@@

This paper has asserted from the beginning that real-world puzzles
pose greater challenges compared to their digital counterparts.
While some intuitive explanations were provided to support this assertion,
a proof hasn't been presented until now. This test ultimately substantiates 
the claim, demonstrating that the performance of the same
algorithm can vary significantly depending on the accuracy of the input data.

@@

Unfortunately the conducted tests reveal that the Comparator we developed in~\cref{document:my_comparator}
and the ``Graph Connection Laplacian'' solution of~\cref{document:GCL}
are not compatible with each other.
A proof supporting this assertion is presented subsequently.

@@

The comparison algorithm described in~\cref{document:my_comparator} outputs a compatibility
shore that goes from 0 to 1.\newline
But the graph connection Laplacian algorithm of~\cref{document:GCL} takes as input a binary value.
Which means that it is necessary to apply a threshold to the input
data to convert them from float to bool.

To find the optimal threshold we solved a small 16 piece puzzle.
And we measured the following 4 values in function of the threshold:

@@

  \item \textbf{correct combination match\% (or c.c match\%):}\newline
  The probability that 2 randomly selected sides matches given that in the correct puzzle
  solution they are actually close to each other. Ideally this should be 1, as we would prefer
  that the comparison never returns false if two pieces are actually connected in the correct solution.

  \item \textbf{limit match\%:}\newline
  Given that this measures has been taken on a 16 piece puzzle,
  the match\% is highly influenced by the correct piece matching together.
  With a bigger puzzle the match\% would be lower (Given that the amount
  of correct couple of sides scales with N, while the amount of
  possible couple of sides scales with \(N^2\). Where N is the number of pieces).\newline
  Limit match\% is an approximation of what the match\%
  would be in the limit for \(N \rightarrow + \infty\).
  This value is obtained by subtracting to match\%
  the probability of choosing randomly the correct side,
  multiplied by the probability that the comparison returns true
  (which is c.c match\%).\newline
  Ideally limit match\% should be almost zero, as we would prefer that the comparison is true only when
  the pieces are actually connected in the correct solution.
  \[limit \: math\% = math\% - \frac{c.c. \: mathc\%}{16 \times 4}\]

@@

Now, let's consider the graph connection Laplacian algorithm of \cref{document:GCL} tasked with solving a 500-piece puzzle
using our Comparator of \cref{document:my_comparator}.
A threshold of 0.425 is chosen;
This implies a limit match\% of 0.04 and a corruption rate of 0.057.
What would this mean in terms of accuracy of the results?

@@

\subsubsection{Corruption Rate Analysis}
\begin{figure}[H]
  \caption{Neighbors comparison vs Corruption rate of graph connection laplacian algorithm of \cref{document:GCL}. Image taken from paper~\cite{GCL} page 34.}\label{fig:GCL_Corruption_Rate}
  \centering
  \includegraphics[height=0.35\textwidth]{pictures/corruption_rate.png}
\end{figure}

@@

Some minor improvements to the comparator can be made by spending some time
tweaking the current algorithm.
However, it is clear that for a task of this nature,
the most viable solution would likely involve
leveraging machine-learning techniques.

@@

\paragraph{Basic notions}

One piece is uniquely identified by his id \texttt{piece\_id}.
The id is an integer that goes from 0 to \mbox{Number of pieces - 1}.
Each piece has 4 sides that can be identified by the side \texttt{side\_id},
an integer that goes from 0 to 3.

\paragraph{Image of each piece}

Inside the folder \texttt{results/pieces} the program will generate one image
for each one of the pieces of the puzzle. The file will be named \texttt{\{piece\_id\}.jpeg}.
An example can be seen in \cref{fig:result_pieces}

@@

\paragraph{Image of each side}

Inside the folder \texttt{results/sides} the program will generate one image 
for each side of each piece. The images will be named \texttt{\{piece\_id\}\_\{side\_id\}.jpeg}.
An example can be seen in \cref{fig:result_sides}

@@

\paragraph{Corners of each piece}
The file \texttt{corners.json} will be generated inside the folder \texttt{results}.
This file will contain a list of pieces.
Each piece has 4 sides, and each side has the coordinates of the two points
that delimit itself.\newline
An example of the generated json can be seen below.

@@

\paragraph{Match for each side}
The file \texttt{connections\_result.json} will be generated
inside the folder \texttt{results}. This file will contain a list of pieces,
each piece has 4 sides, and each side has a link to the side of the piece
that matches it. The link can be null if the side is along the border.\newline
An example of the generated json can be seen below.

@@

All the code used in this project is available on the GitHub repository: \url{https://github.com/lucaSartore/PuzzleSolver}.
